---
title: "Vignette for Kaleigh's package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753KS24)
```

## Vignette Introduction

This is the vignette for my MATH4753 package. 

This package was created so that I could keep a documentation of some of the functions I've used throughout the semester. 

## 1st function: function plotter

The first function is the function plotter. It literally just plots given functions accoridng to the values inputed. 

```{r}
myplot(x=1:10)
```

## 2nd function: central limit thereom

The second function I have is the central limit function (cltu). The central limit theorem (CLT) states that the distribution of sample means approximates a normal distribution as the sample size gets larger, regardless of the population's distribution. The function plots a histogram of the sample mean given a sample size.

```{r}
 mycltu(n=20,iter=100000)
```

## 3rd function: myboot2

The third function I have is myboot2. It is a bootstrap function. Bootstrapping statistics is a form of hypothesis testing that involves resampling a single data set to create a multitude of simulated samples. Those samples are used to calculate standard errors, confidence intervals and for hypothesis testing.
The funtion produces a histogram of bootstrap sample statistics.

```{r}
myboot2(iter=1000, x=20, fun = "mean", alpha=0.05, cx=1.5)
```

## 4th function: myquad

The fourth function I have is the myquad function. It is just a quadratic function which plots values given the input for x.

```{r}
myquad(x = 1:10)
```

## 5th function: ntickets

My fifth function is ntickets. This function is used for a hypothetical airline seat optimization problem and how many tickets should be sold for the flight.

```{r}
 ntickets(N=400, gamma = 0.2, p=0.95)
```


Those are my main 4 functions. 

## dataset: fire

I also have one dataset in the package. It is called fire. It gives the distance a fire is from the nearest fire station, and also measures how much damage was caused by the fire.

```{r}
fire
```





